\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{import}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\name{Parth}{Madhvani}
\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}
\begin{document}
\makecvtitle
\vspace*{-16mm}
\begin{center}\textbf{ Frontend Software Engineer }\end{center}

\begin{center}
{+91 6353649839}~ \quad \href{mailto:madhvaniparth2@gmail.com}{madhvaniparth2@gmail.com} \quad
\href{https://github.com/ParthMadhvani2}{\color{blue}GitHub} \quad
\href{https://parthmadhvani2.github.io/MyPortfolio/}{\color{blue}Portfolio}  \quad
\href{https://www.linkedin.com/in/parthmadhvani2/}{\color{blue}Linkedin}
\end{center}


% ---------- SUMMARY ----------
\section{Summary}
\begin{itemize}[leftmargin=0in, label={}]
\item Innovative Frontend Software Engineer with extensive experience in developing and optimizing user-friendly web applications. Proficient in ReactJS, NextJS, and various UI component libraries. Strong background in full-stack development, including backend technologies and cloud platforms.
\end{itemize}

% ---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0in, label={}]
\normalsize{
    \item \textbf{Languages:} Javascript, Typescript, C++, HTML, CSS
    \item \textbf{Frontend Technologies:} ReactJS, NextJS, REST APIs, Redux, React Query, Framer-motion, Axios, GraphQL
    \item \textbf{UI Component Libraries:} Chakra UI, Shadcn UI, Ant Design, Material UI, styled-components, Tailwind CSS
    \item \textbf{Backend Technologies:} NodeJS, Fastify, Express, Auth, Firebase, Supabase
    \item \textbf{Platforms/Tools:} AWS, Git/GitHub, CI/CD, Vercel, Netlify, Postman, Docker, NPM/Yarn, Version-based releases
    \item \textbf{Other:} WebSockets, tRPC, Jest, Cypress, Strapi
}
\end{itemize}

% ---------- EXPERIENCE ----------
\section{Experience}
\cventry{04/2023 -- present}{Frontend Engineer}{Web3Scope}{(Remote) Bengaluru, India}{}
{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
    \item Developed and optimized reusable components using ReactJS, NextJS, and SCSS, enhancing user engagement.
    \item Created and integrated components with backend APIs, utilizing tables and charts for dynamic data presentation.
    \item Improved application performance and UI through chaos engineering, leading to an 80\% increase in user satisfaction.
\end{itemize}
}

\cventry{05/2024 -- 06/2024}{Full Stack Engineer}{BrainyBeam Info.tech}{(Remote) Ahmedabad, India}{}
{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
    \item Developed FreshFruitHub, an online platform for fresh fruits and vegetables, boosting the company's e-commerce presence.
    \item Implemented key functionalities including user authentication, shopping cart, and wish list features.
    \item Enhanced UI design with best UI/UX practices, improving user experience.
\end{itemize}
}

% ---------- PROJECTS ----------
\section{Projects}
\cventry{Feb 2024 -- Mar 2024}{FramePhase}{\href{https://frame-phase.netlify.app/}{Live Demo} | \href{https://github.com/ParthMadhvani2/FramePhase}{GitHub}}{}{}
{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
    \item Developed FramePhase, a next-gen captions generator app using Next.js 13 and AWS for automated transcription, streamlining the content creation process.
    \item Empowered creators with customizable options and enhanced accessibility, leading to a 25\% increase in user engagement compared to other caption generators.
    \item Tech Stack: Next.js 13, TailwindCSS, WebAssembly, AWS S3 Bucket, AWS Transcribe, Figma
\end{itemize}
}

\cventry{Jan 2024 -- May 2024}{GitHub Landing Page}{\href{https://github-landing.parthmadhvani2.vercel.app/}{Live Demo} | \href{https://github.com/ParthMadhvani2/github-landing}{GitHub}}{}{}
{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
    \item Re-created the GitHub home page using Next.js, significantly improving performance and user experience.
    \item Designed sections in Figma before implementation, ensuring a consistent and professional look.
    \item Tech Stack: Next.js 13, TypeScript, TailwindCSS, Figma, Framer Motion
\end{itemize}
}

% ---------- EDUCATION ----------
\section{Education}
\cventry{2021 -- 2025}{B.Tech in Information Technology}{A.D. Patel Institute of Technology}{Anand, Gujarat}{}{}

\end{document}
